Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-19 article.tex
further edits to intro

The amount of information needed to describe interactions in quantum system would quickly fill up the memory in a classical computer, instead,
a quantum computer can do tasks of this nature efficiently through the use of quantum bits, or qubits to store them \cite{trabesinger2012quantum}.
Since the classical storage unit ‘bit’ is binary system base on 0 and 1, but quantum computer encode them into two distinguishable quantum states,
 and one qubit can represent multiple states once by quantum phenomenon ‘superposition’. Similarly, if we perform a searching algorithm on a classical
 string, the enumerate steps would be the number of bits within this string. Comparably, our processing step will reduce a lot more as we only need to
  compute once in a quantum processor.

>>>>

The amount of information needed to describe interactions in a quantum system would quickly fill up the memory in a classical computer, instead,
a quantum computer can do tasks of this nature efficiently through the use of quantum bits, or qubits to information storage and computation
\cite{trabesinger2012quantum}. Since the classical storage unit ‘bit’ is binary system based on strings of 0s and 1s, but quantum computer encodes
 them into two distinguishable quantum states, and one qubit can represent multiple states once by quantum phenomenon ‘superposition’. Similarly,
 if we perform a searching algorithm on a classical string, the enumerate steps would be the number of bits within this string. Comparably, our
 processing step will reduce a lot more as we only need to compute once in a quantum processor.
